Towards a better predictive model of rest fMRI: benchmarks across multiple phenotypes

### 2017-06-02 rs_study/experiments/paper/paper.tex
iter

\begin{table}[tb]
\small
\begin{tabularx}{\linewidth}{p{1.2cm}|l|c|c|c|c}
    \rowcolor{gray!50}
    Accuracy & COBRE & ADNI & ADNIDOD & ACPI & ABIDE \\ 
    \hline
    \rowcolor{gray!13}
    {\centering $5^{th}$ \\ Percentile} & $74.3\%$ & $62.3\%$ &
    $53.8\%$ & $41.4\%$ & $64.9\%$\\[.1ex]
    Median& $87.1\%$ & $76.2\%$ & $67.1\%$ & $56.4\%$ & $70.2\%$\\
    \rowcolor{gray!13}%
    {\centering $95^{th}$ \\ Percentile} & $94\%$ & $89.1\%$ &
    $77.2\%$ & $68.7\%$ & $73.8\%$\\
    \hline
\end{tabularx}
    \caption{\textbf{
            5th percentile, Median and 95th percentile of accuracy scores in AUC
            over cross-validation folds ($n=100$) across multi rs-fMRI datasets.}
            Accuracy scores reported are specific to optimal choices in
            functional connectivity prediction pipeline: brain atlas,
            connectivity parameterization, linear classifier as outlined
            in -- \autoref{tab:pipeline}.
            Best prediction is achieved with schizophrenia vs control
            discrimination task on COBRE dataset at $87.1\%$ (median) and
            $5^{th}$ percentile of scores are around $74.3\%$ and $95^{th}$
            percentile of scores around $94\%$. Discrimination task on marijuana
            users vs Non-marijuana users are at the chance level of $56.4\%$
            (median) on ACPI
            datasets. We achieved good accuracy with ADNI datasets of $76.2\%$
            (median) discriminating AD vs MCI and autism vs control
            discrimination was acheived of accuracy $70.2\%$ (median).
            vs - versus, AD - Alzheimer's disease, MCI - Mild Cognitive
            Impairment.}
    \label{tab:scores}
\end{table}

@@

\begin{table}[tb]
\small
\begin{tabularx}{\linewidth}{l|p{1.55cm}|c|c|c}
    \rowcolor{gray!50}
    Brain atlas  & Connectome & Classifier & Regions &
    Dimensions \\
    \hline
    DictLearn & Tangent embedding &  SVC-$\ell{_2}$ &  Yes & 60 \\
\end{tabularx}
    \caption{\textbf{
        Prediction choices at each step in resting state functional connectivity
        pipeline: Brain atlas, Connectome, Classifier}.
        The results are outlined after relatively comparing at each step, over the
        choices of classifiers, connectivity parameterization methods and brain
        atlases (pre-defined or data driven atlases) as shown in --
        \autoref{fig:impact_classifier}, \autoref{fig:impact_connectivity} and
        \autoref{fig:impact_atlas}. Functional brain atlases
        learned using Online Dictionary Learning (DictLearn) with
        number of resting state networks=$60$ and spliting networks to regions are
        shown as good choices in the prediction pipeline with Tangent based
        connectivity matrix parameterization and Support Vector Linear
        Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).}
    \label{tab:pipeline}
\end{table}

@@

\begin{figure}
    \centerline{%
	\includegraphics[width=1.\linewidth]{figures/violin_plot_mean_score_region_extraction_ica_dict_kmeans.pdf}%
    }%
    \caption[regions vs non regions]{\textbf{Which is better for prediction:
            Brain regions or Brain networks}
        For each atlas (ICA, DictLearn, KMeans and BASC), we show here the
        best setting for prediction by measuring its impact on prediction
        accuracy for each dataset.

@@

%\begin{figure}
%    \centerline{%
%	\includegraphics[width=.8\linewidth]{n_regions_vs_dimensionality.pdf}%
%    }%
%    \caption{\textbf{Number of regions extracted with dimensionality}
%    %
%    %
%    \label{fig:n_regions_dim}
%    }
%\end{figure}
\paragraph{Choice of brain atlas}

>>>>

\begin{table}[tb]
\small
\begin{tabularx}{\linewidth}{p{1.2cm}|p{1.0cm}|p{0.7cm}|p{1.42cm}|l|l}
    \rowcolor{gray!50}
    \centering{Accuracy} & COBRE & ADNI & ADNIDOD & ACPI & ABIDE \\
    \hline
    \rowcolor{gray!13}
    Median& $87.1\%$ & $76.2\%$ & $67.1\%$ & $56.4\%$ & $70.2\%$\\
    % \rowcolor{gray!13}%
    {\centering $5^{th}$ \\ Percentile} & $74.3\%$ & $62.3\%$ &
    $53.8\%$ & $41.4\%$ & $64.9\%$\\[.1ex]
    \rowcolor{gray!13}
    {\centering $95^{th}$ \\ Percentile} & $94\%$ & $89.1\%$ &
    $77.2\%$ & $68.7\%$ & $73.8\%$\\
    \hline
\end{tabularx}
    \caption{\textbf{
            Median, 5th percentile and 95th percentile of accuracy scores in AUC
            over cross-validation folds ($n=100$) across multi rs-fMRI datasets.}
            Accuracy scores reported are specific to optimal choices in
            functional connectivity prediction pipeline: brain atlas,
            connectivity parameterization, linear classifier as studied
            from -- \autoref{fig:impact_classifier},
            \autoref{fig:impact_connectivity}, \autoref{fig:impact_atlas}.
            Functional brain atlases
            learned using Online Dictionary Learning (DictLearn) with
            number of resting state networks=$60$ and spliting networks to regions are
            shown as good choices in the prediction pipeline with Tangent based
            connectivity matrix parameterization and Support Vector Linear
            Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).
            Best prediction is achieved with schizophrenia vs control
            discrimination task on COBRE dataset at $87.1\%$ (median) and
            $5^{th}$ percentile of scores are around $74.3\%$ and $95^{th}$
            percentile of scores around $94\%$. Discrimination task on marijuana
            users vs Non-marijuana users are at the chance level of $56.4\%$
            (median) on ACPI
            datasets. We achieved good accuracy with ADNI datasets of $76.2\%$
            (median) discriminating AD vs MCI and autism vs control
            discrimination was acheived of accuracy $70.2\%$ (median).
            vs - versus, AD - Alzheimer's disease, MCI - Mild Cognitive
            Impairment.}
    \label{tab:scores}
\end{table}

@@

%\begin{table}[tb]
%\small
%\begin{tabularx}{\linewidth}{l|p{1.55cm}|c|c|c}
%    \rowcolor{gray!50}
%    Brain atlas  & Connectome & Classifier & Regions &
%    Dimensions \\
%    \hline
%    DictLearn & Tangent embedding &  SVC-$\ell{_2}$ &  Yes & 60 \\
%\end{tabularx}
%    \caption{\textbf{
%        Prediction choices at each step in resting state functional connectivity
%        pipeline: Brain atlas, Connectome, Classifier}.
%        The results are outlined after relatively comparing at each step, over the
%        choices of classifiers, connectivity parameterization methods and brain
%        atlases (pre-defined or data driven atlases) as shown in --
%        \autoref{fig:impact_classifier}, \autoref{fig:impact_connectivity} and
%        \autoref{fig:impact_atlas}. Functional brain atlases
%        learned using Online Dictionary Learning (DictLearn) with
%        number of resting state networks=$60$ and spliting networks to regions are
%        shown as good choices in the prediction pipeline with Tangent based
%        connectivity matrix parameterization and Support Vector Linear
%        Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).}
%    \label{tab:pipeline}
%\end{table}

@@

\begin{figure}
    \centerline{%
	\includegraphics[width=1.\linewidth]{figures/regions_nonregions_difference_distribution.pdf}%
    }%
    \caption[regions vs non regions]{\textbf{Which is better for prediction:
            Brain regions or Brain networks}
        For each atlas (ICA, DictLearn, KMeans and BASC), we show here the
        best setting for prediction by measuring its impact on prediction
        accuracy for each dataset.

@@

\begin{figure}
    \centerline{%
	\includegraphics[width=0.5\paperwidth]{figures/brainrois.pdf}%
    }%
    \caption{\textbf{Brain regions/parcellations using ICA, DictLearn, KMeans,
        Ward}
    %
    %
    \label{fig:brain_rois}
    }
\end{figure}
\paragraph{Choice of brain atlas}
